Subsegmental language detection in Celtic language text

### 2014-06-27 codeswitch-cltw-2014/codeswitch_camera_ready.tex
review 2.8
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@55023 72bbbca6-d526-0410-a7d9-f06f51895060

After restricting the predicted languages to be amongst the two in the dataset, we used the character bigram and then trigram probabilities to predict the detected language for each token, some rules like in section~\ref{sec:method} were followed which included that the span of a segment or a code-switched phrase is more than a word, the social media non-language entities such as the hashtags, usernames and urls do not make a difference.

>>>>

Restricting the predicted languages to be amongst the two in the dataset was a decision made to identify the language pairs in a better fashion, both by our techniques and by the competitive tools too. Then we used the character bigram and then trigram probabilities to predict the detected language for each token. Rules in section~\ref{sec:method} were followed for the text processing and chunking part of the method.
%which included that the span of a segment or a code-switched phrase is more than a word, the social media non-language entities such as the hashtags, usernames and urls do not make a difference.
